### 2014-03-13 Draft/evaluation.tex
Added Skelton for Kunal

\begin{itemize}
	\item\textbf{RQ1}: What are the precision and recall of \tool\  in
	identifying temporal constraints from sentences written in natural language?
	\item\textbf{RQ2}: What is the accuracy of \tool\ in inferring temporal constraints from specification sentences in the API documents?
	\item\textbf{RQ3}: How do the constraints inferred by our approach compare with the typed-enforced temporal constraints?

@@

To answer RQ1, we measure the number of true positives ($TP$), false positives ($FP$), true negative ($TN$), and false negatives ($FN$)
in identifying the specification sentences by \tool.
We define specification sentence as a sentence describing a temporal constraints.
We define the $TP$, $FP$, $TN$, and $FN$ of \tool\ as follows:

\begin{enumerate}
	\item $TP$: A sentence correctly identified by \tool\ as specification sentence.
	\item $FP$: A sentence incorrectly identified by \tool as specification sentence.
	\item $TN$: A sentence correctly identified by \tool\ as not a specification sentence.
	\item $FN$: A sentence incorrectly identified by \tool\ as not a specification sentence.
\end{enumerate}

In statistical classification~\cite{Olson08}, $Precision$ is defined as a ratio of
number of true positives to the total number of items reported to be true,
$Recall$ is defined as a ratio of number of true positives to the total number
of items that are true. $F-score$ is defined as the weighted harmonic mean of 
$Precision$ and $Recall$. Higher value of $Precision$, $Recall$, and $F-Score$
are indicative of higher quality of the specification statements inferred using 
\tool. based on the calculation of $TP$, $FP$, $TN$, and $FN$ of \tool\ defined
previously we computed the $Precision$, $Recall$, and $F-Score$ of \tool\ as follows:

@@

To answer RQ2, we checked the temporal constraints inferred from specification sentences by \tool.
We measure $accuracy$ of \tool as the ratio of the total number of temporal constraints that
are correctly inferred by \tool to the total number of specification sentences.

@@

In this section, we quantify the effectiveness of \tool\ in identifying specification sentences by answering RQ1.
Table~\ref{tab:results} shows the effectiveness of \tool\ in identifying specification sentences.
Column ``API'' lists the names of the subject API. 
Column ``Methods'' and ``Sentences'' lists the number of methods and sentences in each subject API's.
Column ``\tool\ Ann'' lists the number of sentences identified by \tool\ as constraint sentences. 
Columns ``TP'', ``FP'', ``TN'', and ``FN'' represent the number of \CodeIn{true positives}, \CodeIn{false positives}, \CodeIn{true negatives}, and \CodeIn{false negatives}, respectively. 
Columns ``P(\%)'', ``R(\%)'', and ``F-Score(\%)'' list percentage values of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively. 
Our results show that, out of 3,909 sentences, \tool\ effectively identifies specification sentences with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.

%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence. \textbf{A example goes here}
We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence (producing false positives). For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class. \tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''. However \tool\ fails to make the distinction that it happens internally (enforced within the body) in the method. \tool, thus incorrectly identifies the sentence as a specification sentence.

Another major source of FPs is the incorrect parsing of sentences by the underlying NLP infrastructure and/or inadequacy of generic dictionaries for synonym analysis. For instance, consider the sentence ``\textit{If this stream has an associated channel then the channel is closed as well.}'' from the \CodeIn{close} method description from \CodeIn{FileOutputStream}. The sentence describes an effect that happens as a result of calling the \CodeIn{close} method and does not describe any temporal constraint. However, \tool\ annotates the sentence as a specification sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''. This incorrect matching in turn causes \tool to incorrectly annotate the sentence as specification sentence because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}. We observed 8 instances of previously described example in our results.

@@

We next present an example to illustrate how \tool\ fails identify a specification sentence (producing false negative). False negatives are undesirable in the context of our problem domain, because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents. Furthermore, an overwhelming number of false negatives works against the usefulness of \tool. For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class. The sentence describes the constraint in terms of invoking the same method again. Although \tool\ correctly identifies the method \CodeIn{close} in the sentence, \tool\ currently does not support temporal constraint on the same method. Aforementioned, limitation causes \tool\ to not identify the statement as a specification constraint.

@@

In this section, we evaluate the effectiveness of \tool\ in inferring specification sentences from API documents.

@@

\subsection{Threats to Validity}
\label{sub:threats_to_validity}
Threats to external validity primarily include the degree to which the subject documents used in our evaluations are representative of true practice. To minimize the threat, we used API documents of two representative commercial REST API: one dealing with online storage and the other \textbf{TBD}. The \amazon documents describe one of the most popularly used and online storage APIs. We also used the \textbf{TBD}. Furthermore, the difference in the functionalities provided by the two projects also address the issue of over fitting our approach to a particular type of API. The threat can be further reduced by evaluating our approach on more subjects.

>>>>

\begin{itemize}
	\item\textbf{RQ1}: What are the precision and recall of \tool\ in identifying temporal constraints from sentences written in natural language?
	\item\textbf{RQ2}: What is the accuracy of \tool\ in inferring temporal constraints from constraint sentences in the API documents?
	\item\textbf{RQ3}: How do the constraints inferred by our approach compare with the typed-enforced temporal constraints?

@@

To answer RQ1, we measure the number of true positives ($TP$), false positives ($FP$), true negative ($TN$), and false negatives ($FN$)
in identifying the constraint sentences by \tool.
We define constraint sentence as a sentence describing a temporal constraints.
We define the $TP$, $FP$, $TN$, and $FN$ of \tool\ as follows:

\begin{enumerate}
	\item $TP$: A sentence correctly identified by \tool\ as constraint sentence.
	\item $FP$: A sentence incorrectly identified by \tool as constraint sentence.
	\item $TN$: A sentence correctly identified by \tool\ as not a constraint sentence.
	\item $FN$: A sentence incorrectly identified by \tool\ as not a constraint sentence.
\end{enumerate}

In statistical classification~\cite{Olson08}, $Precision$ is defined as a ratio of
number of true positives to the total number of items reported to be true,
$Recall$ is defined as a ratio of number of true positives to the total number
of items that are true. $F-score$ is defined as the weighted harmonic mean of 
$Precision$ and $Recall$. Higher value of $Precision$, $Recall$, and $F-Score$
are indicative of higher quality of the constraint statements inferred using 
\tool. based on the calculation of $TP$, $FP$, $TN$, and $FN$ of \tool\ defined
previously we computed the $Precision$, $Recall$, and $F-Score$ of \tool\ as follows:

@@

To answer RQ2, we checked the temporal constraints inferred from constraint sentences by \tool.
We measure $accuracy$ of \tool as the ratio of the total number of temporal constraints that
are correctly inferred by \tool to the total number of constraint sentences.

@@

In this section, we quantify the effectiveness of \tool\ in identifying constraint sentences by answering RQ1.
Table~\ref{tab:results} shows the effectiveness of \tool\ in identifying constraint sentences.
Column ``API'' lists the names of the subject API. 
Column ``Methods'' and ``Sentences'' lists the number of methods and sentences in each subject API's.
Column ``\tool\ Ann'' lists the number of sentences identified by \tool\ as constraint sentences. 
Columns ``TP'', ``FP'', ``TN'', and ``FN'' represent the number of \CodeIn{true positives}, \CodeIn{false positives}, \CodeIn{true negatives}, and \CodeIn{false negatives}, respectively. 
Columns ``P(\%)'', ``R(\%)'', and ``F-Score(\%)'' list percentage values of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively. 
Our results show that, out of 3,909 sentences, \tool\ effectively identifies constraint sentences with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.

%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence. \textbf{A example goes here}
We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence (producing false positives). For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class. \tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''. However \tool\ fails to make the distinction that it happens internally (enforced within the body) in the method. \tool, thus incorrectly identifies the sentence as a constraint sentence.

Another major source of FPs is the incorrect parsing of sentences by the underlying NLP infrastructure and/or inadequacy of generic dictionaries for synonym analysis. For instance, consider the sentence ``\textit{If this stream has an associated channel then the channel is closed as well.}'' from the \CodeIn{close} method description from \CodeIn{FileOutputStream}. The sentence describes an effect that happens as a result of calling the \CodeIn{close} method and does not describe any temporal constraint. However, \tool\ annotates the sentence as a constraint sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''. This incorrect matching in turn causes \tool to incorrectly annotate the sentence as constraint sentence because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}. We observed 8 instances of previously described example in our results.

@@

We next present an example to illustrate how \tool\ fails identify a constraint sentence (producing false negative). False negatives are undesirable in the context of our problem domain, because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents. Furthermore, an overwhelming number of false negatives works against the usefulness of \tool. For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class. The sentence describes the constraint in terms of invoking the same method again. Although \tool\ correctly identifies the method \CodeIn{close} in the sentence, \tool\ currently does not support temporal constraint on the same method. Aforementioned, limitation causes \tool\ to not identify the statement as a constraint constraint.

@@

In this section, we evaluate the effectiveness of \tool\ in inferring constraint sentences from API documents.

@@

\subsection{Threats to Validity}
\label{sub:threats_to_validity}
Threats to external validity primarily include the degree to which the subject documents used in our evaluations are representative of true practice. To minimize the threat, we used API documents of two different API's: JDK \CodeIn{java.io} and \amazon. On one hand Java is a widely used programming language and \CodeIn{java.io} and is one of the main packages. In contrast, \amazon\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language. Furthermore, the difference in the functionalities provided by the two API's also address the issue of over fitting our approach to a particular type of API. The threat can be further reduced by evaluating our approach on more subjects.
